State of the Art in Concurrent Priority Queues \\ Student Paper for Seminar in Algorithms 2013W \\ Technical University of Vienna

### 2014-03-21 paper/paper.Rnw
Integrate results plot

\usepackage{acronym}
\usepackage[backend=bibtex]{biblatex}
\usepackage[usenames,dvipsnames]{color}
\usepackage{comment}
\usepackage[pdfborder={0 0 0}]{hyperref}
\usepackage[utf8]{inputenc}
\usepackage{listings}

@@

>>>>

\usepackage{acronym}
\usepackage[backend=bibtex]{biblatex}
\usepackage[usenames,dvipsnames]{color}
\usepackage{comment}
\usepackage{graphicx}
\usepackage[pdfborder={0 0 0}]{hyperref}
\usepackage[utf8]{inputenc}
\usepackage{listings}

@@

\begin{center}
<<results = tex, echo = FALSE>>=
library(Rmisc)
library(ggplot2)
library(plyr)
library(scales)

figfile <- "fig.eps"

# install.packages(c("Rmisc", "ggplot2", "plyr"))

df <- read.csv("../results/results.csv")
colnames(df) <- c("kernel", "p", "throughput")

df$throughput <- df$throughput/1E6

df2 <- ddply(df, .(kernel, p), summarize, mean = mean(throughput),
             lower = CI(throughput)[[3]], upper = CI(throughput)[[1]])

# Bar graph

# dodge <- position_dodge(width=0.9)
# p <- ggplot(df2, aes(x = factor(p), y = mean, fill = factor(kernel))) +
#             geom_bar(stat = "identity", position = dodge) +
#             geom_errorbar(aes(ymin = lower, ymax = upper), position = dodge, width = 0.3) +
#             ylab("throughput [Mops/s]") +
#             xlab("number of threads")

p <- ggplot(df2, aes(x = p, y = mean, color = kernel, shape = kernel)) +
            geom_line() +
            geom_point(size = 4) +
#            geom_errorbar(aes(ymin = lower, ymax = upper), width = 0.3) +
            ylab("throughput in Mops/s") +
            xlab("number of threads") +
# Themes
            theme_bw() +
            theme(axis.text = element_text(size = 16),
                  axis.title = element_text(size = 18),
                  legend.text = element_text(size = 16),
                  legend.title = element_text(size = 18),
                  legend.position = c(1, 1),
                  legend.justification = c(1, 1),
                  legend.background = element_rect(fill = alpha("black", 0)))

postscript(file = figfile, paper = "special", width = 10, height = 5, horizontal = FALSE)
plot(p)
invisible(dev.off())
cat("\\includegraphics[width = \\textwidth]{", figfile, "}\n\n", sep = "")

# PDF output

# pdf("abcd.pdf", width=10, height=10)
# plot(p)
# dev.off()
@
\end{center}
